---
title: "Sejong_poll : Data in Korean"
author: "coop711"
date: '`r Sys.Date()`'
output: html_document
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(pander)
library(knitr)
options(width = 180)
```

## Data input

```{r, data}
load("./sejong_poll_data.RData")
```

### Data 

```{r, dataframe}
kable(sejong_poll_2[4:1])
```

### Korean Factor Levels

```{r, labels in Korean}
sejong_poll_kr <- sejong_poll_2
sejong_poll_kr$vote <- factor(sejong_poll_kr$vote, 
                              levels = c("Yes", "No"), 
                              labels = c("찬성", "반대"))
class_labels_kr <- c("대신 등", "3품이하현직", "3품이하전직", "수령", "품관촌민") 
sejong_poll_kr$class <- factor(sejong_poll_kr$class, 
                               levels = class_labels, 
                               labels = class_labels_kr)
region_labels_kr <- c("서울", "유후사", "경기", "평안", "황해", "충청", "강원", "함길", "경상", "전라")
sejong_poll_kr$region <- factor(sejong_poll_kr$region, 
                                levels = region_labels, 
                                labels = region_labels_kr)
vnames_kr <- c("소계", "찬반", "계급", "지역")
# names(sejong_poll_kr) <- vnames_kr
kable(sejong_poll_kr[4:1])
```

<P style = "page-break-before:always">

```{r, echo = FALSE}
kable(sejong_poll_kr[4:1], 
      align = NULL, 
      col.names = vnames_kr[4:1])
```

<P style = "page-break-before:always">

### Cross Tables

```{r, cross tables}
tbl_vote <- xtabs(counts ~ vote, 
                  data = sejong_poll_kr)
tbl_class <- xtabs(counts ~ class, 
                   data = sejong_poll_kr)
tbl_region <- xtabs(counts ~ region, 
                    data = sejong_poll_kr)
tbl_vote_class <- xtabs(counts ~ vote + class, 
                        data = sejong_poll_kr)
tbl_vote_region <- xtabs(counts ~ vote + region, 
                         data = sejong_poll_kr)
tbl_vote_class_region <- xtabs(counts ~ vote + class + region, 
                               data = sejong_poll_kr)
ftbl_vote_class_region <- ftable(xtabs(counts ~ vote + class + region,
                                       data = sejong_poll_kr))
```

### Array

We can set up the data as an array

```{r, array structure}
sejong_poll_array <- xtabs(counts ~ vote + class + region, 
                           data = sejong_poll_kr,
                           drop.unused.levels = TRUE)
str(sejong_poll_array)
sejong_poll_array
```

## Votes

### Total

Check the total vote with xtabs()

```{r, total yes or no}
vote_total <- xtabs(counts ~ vote, 
                    data = sejong_poll_kr)
kable(t(as.matrix(vote_total)), 
      caption = "총계")
# format(prop.table(vote_total)*100, digits = 3, nsmall = 1)
kable(t(as.matrix(format(prop.table(vote_total) * 100, 
                         digits = 3, nsmall = 1))), 
      caption = "백분율", 
      align = rep("r", 2))
vote_total_2 <- apply(sejong_poll_array, 
                      MARGIN = 1, 
                      FUN = sum)
# kable(t(as.matrix(vote_total_2)))
kable(t(as.matrix(vote_total_2)), 
      caption = "총계")
```

### Vote by class

```{r, by class}
vote_class <- xtabs(counts ~ vote + class, 
                    data = sejong_poll_kr)
kable(vote_class, 
      caption = "계급별")
vote_class_a <- apply(sejong_poll_array, 
                      MARGIN = 1:2, 
                      FUN = sum)
kable(vote_class_a, 
      caption = "계급별")
```

### Commons vs Bureaucrats

We need to analyse Commons separately. 

```{r, commons vs bureaus}
sejong_poll_kr$class_2 <- 
  factor(ifelse(sejong_poll_kr$class == "품관촌민", "품관촌민", "관료"),
         levels = c("관료", "품관촌민"))
kable(sejong_poll_kr[c(4, 3, 5, 2, 1)])
str(sejong_poll_kr)
```

Compare the votes by `class_2`,  (Bureaucrats vs Commons)

```{r, vote by class_2}
vote_class_2 <- xtabs(counts ~ vote + class_2, 
                      data = sejong_poll_kr)
kable(vote_class_2, 
      caption = "관료와 품관촌민")
vote_class_2_a <- cbind("관료" = rowSums(vote_class_a[, -5]), 
                        "품관촌민" =  vote_class_a[, 5])
kable(vote_class_2_a, 
      caption = "관료와 품관촌민")
```

Add subtotals to the margins, 

```{r, subtotals}
vote_class_2_am <- addmargins(vote_class_2)
colnames(vote_class_2_am)[3] <- "계"
rownames(vote_class_2_am)[3] <- "계"
kable(vote_class_2_am, align = rep("r", 3))
```

Compute the marginal proportions. Note the use of `digits = 3` and `nsmall = 1`.

```{r, proportions}
kable(format(prop.table(vote_class_2, margin = 2) * 100, 
             digits = 3, nsmall = 1), 
      caption = "관료와 품관촌민", 
      align = rep("r", 2))
```

### Votes by region with respect to class_2 

Count the vote by region class_2 wise.

```{r, region w.r.t class_2}
class_2 <- sejong_poll_kr$class_2
vote_region_bureaus <- xtabs(counts ~ vote + region, 
                             data = sejong_poll_kr, 
                             class_2 == "관료", drop = TRUE)
kable(vote_region_bureaus, 
      caption = "집계(관료)")
# xtabs(counts ~ vote + region, data = sejong_poll_kr[class_2 == "Bureaus", ], drop = TRUE)
vote_region_commons <- xtabs(counts ~ vote + region, 
                             data = sejong_poll_kr, 
                             class_2 == "품관촌민", 
                             drop.unused.levels = TRUE)
kable(vote_region_commons, 
      caption = "집계(품관촌민)", 
      align = rep("r", 9))
```

Seoul has three times more Bureaucrats than other regions, so analyse further.

```{r, Seoul}
region <- sejong_poll_kr$region
vote_seoul_class <- xtabs(counts ~ vote + class, 
                          data = sejong_poll_kr, 
                          region == "서울", 
                          drop.unused.levels = TRUE)
kable(vote_seoul_class, caption = "서울")
kable(format(prop.table(vote_seoul_class, margin = 2) * 100, 
             digits  = 3, nsmall = 1), 
      caption = "서울", 
      align = rep("r", 3))
```

Chungcheong's case.

```{r, Chungcheong}
vote_chung_class <- xtabs(counts ~ vote + class, 
                          data = sejong_poll_kr, 
                          region == "충청", 
                          drop.unused.levels = TRUE)
kable(format(prop.table(vote_chung_class, margin = 2) * 100, 
             digits = 3, nsmall = 1), 
      caption = "충청", 
      align = rep("r", 3))
```

- Save the working directory image.

```{r, save}
save.image(file = "sejong_poll_data_kr.RData")
```
