---
title: "Weighted Dice Very Basics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Objects

## Assignment

```{r}
die1 <- c(1, 2, 3, 4, 5, 6)
die2 <- 1:6
die1 == die2
die <- die2
ls()
```

## Vectorized Operations

Check how the mathematical operations are regarded as functions, and how to bring up help pages 

```{r}
die - 1
die / 2
die * die
1:2
1:4
die + 1:2
die + 1:4
die %*% die
die %o% die
outer(die, die)
# help("%*%")
# help("%o%")
# ?`%*%`
# ?outer
```

# Functions

```{r}
round(3.1415)
round(3.1415, digits = 2)
factorial(3)
mean(1:6)
mean(die)
sd(die)
round(mean(die), digits = 2)
```

## Sampling

`x` for the population, `size` for the sample size. 
Note how the arguments are recognized.

```{r}
# ?sample
sample(die)
sample(x = 1:4, size = 2)
sample(x = die, size = 1)
sample(x = die, size = 1)
sample(x = die, size = 1)
sample(die, size = 1)
# round(3.1415, corners = 2)
args(round)
round(3.1415, digits = 2)
sample(die, 1)
sample(size = 1, x = die)
# ?sample
```

## Sample with Replacement

```{r}
sample(die, size = 2)
sample(die, size = 2, replace = TRUE)
sample(die, size = 2, replace = TRUE)
dice <- sample(die, size = 2, replace = TRUE)
dice
sum(dice)
```


# Writing Your Own Functions

## The Function Constructor

Simulate sum of two tosses of a die, or the sum of two dice thrown. The difference between `roll()` and `roll`.

```{r}
roll <- function() {
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE)
  sum(dice)
}
roll()
roll
```

## Arguments

How to implement an input variable, Why we need to set up a default value.

```{r}
roll2 <- function(bones) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
roll2(bones = 1:4)
roll2(bones = 1:5)
roll2(1:20)
# roll2()
```

## Default Value

```{r}
roll2 <- function(bones = 1:6) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
roll2()
```

## Dump and Source

```{r}
dump(list = c("roll", "roll2"), file = "./roll.R")
rm(list = ls())
ls()
source("./roll.R")
ls()
```

